Project-II by Group Sydney

### 2015-12-20 Projet II/report/paper.tex
Add last results

\subsection{Bootstrap Aggregation}

As we have seen in the lecture, decision trees are good because the training and the prediction is quite fast, even with many features or large dataset but have a high variance. The idea of decision trees, is to have a several questions where to answer yes/no and to move in the tree. At the end, the leaves give the corresponding class. To construct this list of questions, we divide recursively the space in a way to minimize the cost of impurity (depending of the threshold to find and the current feature). The depth of the tree is a parameter.

@@

>>>>

\subsection{Bootstrap Aggregation (Bagging)}

As we have seen in the lecture, decision trees are good because the training and the prediction is quite fast, even with many features or large dataset but have a high variance and might overfit. The idea of decision trees, is to have a several questions where to answer yes/no and to move in the tree. At the end, the leaves give the corresponding class. To construct this list of questions, we divide recursively the space in a way to minimize the cost of impurity (depending of the threshold to find and the current feature). The depth of the tree is a parameter.

@@

The idea of random forests is similar than with bagging in a sense that we train several trees and take the average predictions. Like bagging, each trees have trained on a subset of the dataset. However, there is another aspect in random forest that bagging doesn't have: for each split, instead of searching among the overall features, we search only among a random subset of features. The size of this subset is a parameter $m$ as well as the depth tree and the number of trees, like in bagging. Like bagging, random forests are useful because they help reducing the variance and the overfiting. But the more interesting ideas is to select only a subset of the features in the split process.
